---
title: "Pratical Machine Learning project"
author: "sungyoul park"
output: html_document
---
***
###Step 1: Data reading and cleaning 

* In data sets,there are lot's of invalid values such as #DIV/O! and  alomst empty values in some of covariantes which don't helpful to analysis
* Replacing invalid value as 'Na' and exclude covariates which have empty value more than 15000  

```{r, message=FALSE}
library(kernlab)
library(caret)

read.training= read.csv("~/workspace/ml/pml-training.csv",header = TRUE,
                   stringsAsFactors =FALSE, na.strings = c("NA","NaN"," ", "#DIV/0!"))
read.testing = read.csv("~/workspace/ml/pml-testing.csv",header = TRUE,
                   stringsAsFactors =FALSE, na.strings = c("NA","NaN"," ", "#DIV/0!"))

read.training$classe <- as.factor(read.training$classe)
read.testing$problem_id <- as.factor(read.testing$problem_id)

training <- read.training[,colSums(is.na(read.training)) < 15000]
testing <- read.testing[,colSums(is.na(read.testing)) < 20]

```

###Step 2:  Paritioning training data 

* Excluding appraently irrevalent covariates("X","user_name","raw_timestamp_part_1","raw_timestamp_part_2", "cvtd_timestamp","new_window",num_window") to reduce processing time and avoide overfiting issue
* Partition training with training.classe and testing.classe as 7:3 ratio

```{r}
training <-training[,-c(1:7)]
testing <- testing[,-c(1:7)]

intrain <-createDataPartition(y = training$classe,p = 0.7,list = FALSE)
training.classe <- training[intrain,]
testing.classe <- training[-intrain,]
```

### Step 3: Fit modeling and validation

*Fit Modeling with **random forest** and **3-fold cross validations** to predict all other prdictors
*Apply this model to testing.classe dataset to verify the model fittness and this Random forest model's accurary is almost closed to 1 (0.9966)
```{r,results='hide'}
set.seed(1971)
fitControl <- trainControl(method="cv",number=3,verboseIter=TRUE,allowParallel = TRUE)
modelFit <- train(classe ~., data=training.classe,method="rf",verbose=FALSE,trControl = fitControl)
```
```{r,message=FALSE}
prediction <- predict(modelFit, newdata = testing.classe)
confusionMatrix(prediction,testing.classe$classe)
```


### Final Step: prediction 
* predict the classe type of 20 person in test data set and display the result
```{r}
answers <- predict(modelFit,newdata=testing)
test <- list('problem_id'=testing$problem_id,'classe'=answers)
final_result <- as.data.frame(test)
print(final_result)
```


